%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{russell}
% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% russell Colors: russell-emerald, russell-skyblue, russell-red, russell-pink, russell-orange
%                 russell-nephritis, russell-concrete, russell-darknight, russell-purple
\colorlet{russell}{russell-orange}
% Uncomment if you would like to specify your own color
% \definecolor{russell}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
 \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with russell color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,noedge,right]{./profile.jpg}
\name{Hyeong Seon}{Yoo}
% \position{Software Architect{\enskip\cdotp\enskip}Security Expert}
\address{Parañaque City, National Capital Region, Philippines}

\dateofbirth{1999-12-30}
\mobile{09082279581}
\email{sylvesteryoo@naver.com}
\github{github.com/hexagonforce\\}

%\homepage{www.posquit0.com}
\linkedin{https://www.linkedin.com/in/hyeongseonyoo/}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Simplicity is deceptively complicated."}
\recipient
  {Ericsson-LG}
  {12-13F, LG Gasan Digital Center,
189, Gasan digital 1-ro, Geumcheon-gu,
Seoul, 08503, Republic of Korea}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Packet Core R{\&}D Software Developer}
% How the letter is opened
\letteropening{Dear Sir/Madam,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
 %	BIBLIOGRAPHY
 %-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[L]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Hyeong Seon Yoo ~~~·~~~ Cover Letter}
  {}

\makelettertitle

\begin{cvletter}
    Thank you for this opportunity for the Ericsson Packet Core R\&D developer position. The two areas of interest that I have worked on for the past few years are C\+\+ and networking. I particularly enjoy discovering new features related to C\+\+ programming every day, such as the many features of the Standard Template Library. I think I will be a strong addition to the team; in addition to my academic achievements, my experience and communication skills will be an asset to your company.

    I have a strong background in data structures and algorithms through my participation in various ICPC competitions through my school's programming team. Throughout these competitions, I have used the C\+\+ and Python languages extensively. I have also used C++ and Python to accomplish school projects and my thesis. I also have the patience and determination to learn from difficult code and documentation, which culminated in my publication of papers on Software-defined Networking in IEEE recognized conferences on Software-defined Networking.

    While I might not be directly experienced in 5G or Packet Core networking, I have the fundamentals and research experience that will be an asset to your company. In addition, my primary field of interest in computer science is networking and lower-level programming, which is aligned with your company's vision of a more connected future. I hope for your consideration, and I would love to work with you in the future.
\end{cvletter}


\makeletterclosing
\end{document}
